\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-08 chapters/1_intro.tex
Rewrite pseudocode and move contr. gr. to Appendix

Our main contribution is a review framework for graph clustering that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract). 
Various existing clustering algorithms, previously introduced in \cite{levinkov2017comparative,wolf2018mutex,kardoostsolving,lance1967general}, share the general procedure defined in our framework, but differ in the way in which the interaction between clusters is updated after each agglomeration step. Moreover, we also introduce new variations of these algorithms by allowing the possibility of enforcing mutual-exclusion relationships between clusters.

We evaluate the performances of these different agglomerative clustering algorithms on image instance segmentation of 2D urban scenes (CityScapes dataset) and 3D biological image stacks (CREMI neuron segmentation challenge), by comparing achieved scores, efficiency and robustness to noisy edge weights. 
% \TODO{Chapters description}

>>>>

Our first contribution is a review framework for graph clustering (Sec. \ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract). 
We show that various existing partitioning algorithms \cite{levinkov2017comparative,wolf2018mutex,kardoostsolving,lance1967general} can be reformulated in our framework, so that they share a general procedure but differ in the way inter-cluster interaction is updated after each iteration. Moreover, this framework allows us to introduce new variations of these algorithms that also enforce mutual-exclusion relationships between clusters.

Finally, the algorithms included in the framework are evaluated on an instance segmentation task, both on 3D biological image stacks (Sec. \ref{sec:neuro_segm_exp}) and 2D urban scenes (Sec. \ref{sec:cityscapes_exp}). Our analysis highlights strengths and weaknesses of each algorithm by comparing their robustness to noise, efficiency and inclination to output a well balanced graph partitioning.

### 2019-05-08 chapters/2_rel_work.tex
Update figures; start getting rid of update rules
Rewrite pseudocode and move contr. gr. to Appendix

\textbf{Edge detection} also experienced recent noticeable progress \cite{xie2015holistically,kokkinos2015pushing}. This is nicely illustrated by the evolution of neuron segmentation for connectomics, a field of neuroscience we also address in our experiments. CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in deep learning and data augmentation lead to much more refined boundary detection \cite{lee2017superhuman,meirovitch2016multi,ciresan2012deep}. 
% or trained an end-to-end watershed region growing algorithm \cite{wolf2017learned}.  
Subsequent postprocessing and superpixel-merging outputs final instances. Some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy. The lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time. A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
% \SOURCE{SSHMT} Check Funke proposals

\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts. 
Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters; whereas the optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy. \TODO{Roman, Cocoons, Benjamin?}
On the other hand, several segmentation pipelines use classical HC linkage criteria, e.g. average linkage \cite{liu2018affinity,lee2017superhuman} or median \cite{funke2018large}. The GALA algorithm in \cite{nunez2013machine,knowles2016rhoananet} features instead a linkage learned by a neural network.

\textbf{Clustering of signed graphs} is another important line of research with the goal of balancing a graph with both attractive and repulsive cues. Finding an optimally balanced clustering has a long history in the field of combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
The name \emph{correlation clustering} was coined by \cite{bansal2004correlation} that also showed its NP-hardness, while its connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problem instances of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger problems.
\TODO{Cannot-link constraints?}
% Missing: Funke proposals, discussion about cannot-link constraints!!!

\UPDATE{This work combines the clustering algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a simple generalized framework for agglomerative clustering and evaluate them on an instance segmentation task by adopting ideas and CNN architectures from \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels and boundary evidence between instances.}

>>>>

\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and \UPDATE{biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}}. In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
% CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in deep learning and 
% the introduction of new architectures lead to a much more refined boundary detection. 
% or trained an end-to-end watershed region growing algorithm \cite{wolf2017learned}.  
% Subsequent postprocessing and superpixel-merging outputs final instances. 
some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time. A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
% \SOURCE{SSHMT} Check Funke proposals

\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts. 
Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters. 
% \TODO{Roman, Cocoons, Benjamin?}
The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HC linkage criteria, e.g. average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a neural network \cite{nunez2013machine,knowles2016rhoananet}.

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
% \TODO{Cannot-link constraints?}
% Missing: Funke proposals, discussion about cannot-link constraints!!!

This work reformulates the clustering algorithms of \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient} in a general framework and adopt ideas from the proposal-free methods \cite{liu2018affinity,wolf2018mutex,funke2018large} to predict long-range relationships between pixels.
